Workflow

### 2014-08-01 Workflow/Workflow.Rmd
PostProcess uses -S instead of -R. -R is still an option.

### Post-process the results
* Run `Scripts/PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
    + `Packages/EconData/data/<Source>_Coeffs.rda` and
    + `Packages/EconData/data/<Source>_Fitted.rda`.

>>>>

### Post-process the results
* Run `Scripts/PostProcess.R -S <Source>` on a node of dahl to create:       
    + `Packages/EconData/data/<Source>_Coeffs.rda` and
    + `Packages/EconData/data/<Source>_Fitted.rda`.
